The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-16 paper.tex
update

 The left column of \Cref{fig__profile} shows the profiles cut at\
 the positive z-axis in \Cref{fig__jetI5+ismSeed3-45deg}.\
 The temperature profile in the left column indicates that\
 most of the region between the forward shock and the turbulent zone\
 is around 0.3-0.4 keV, similar to that observed by \citet{Miller2016} and \citet{Kataoka2018}.

 Followed by the forward shock is a turbulent and hot plasma.\
 The full extent of the hot plasma is approximately agree with the observation \citep{Su2010}.
 Moreover, the temperature of the plasma is high as 2 keV, comparable to that of the \textit{Fermi} bubbles\
 by observing X-ray absorption lines through the hot\
 gaseous halo along many different sight lines in the sky \citep{Miller_2013}.\

 % which we will interpret as the \textit{Fermi} bubbles.\

>>>>

 The temperature profile (left column of \Cref{fig__profile}) along the positive z-axis in\
 \Cref{fig__jetI5+ismSeed3-45deg} indicates that\
 most of the region between the forward shock and the turbulent zone\
 is around 0.3-0.4 keV, similar to that observed by \citet{Miller2016} and \citet{Kataoka2018}.

 Followed by the forward shock is a turbulent and hot plasma.\
 As shown in the temperature or density slices of the fiducial run,\
 the full extent of the turbulent plasma is approximately agree with\
 that of the \textit{Fermi} bubbles \citep{Su2010}.
 Also, the temperature of the plasma is as high as 2 keV, comparable to that inside the \textit{Fermi} bubbles\
 by observing X-ray absorption lines through the hot\
 gaseous halo along many different sight lines in the sky \citep{Miller_2013}.\
 We also note that the turbulence within the hot plasma is in pressure balance with the external medium,\
 suggesting that the outer edge of the \textit{Fermi} bubbles\
 is a tangling contact discontinuity rather than a shock.

 The most interesting finding is that there is a innermost bubbles\
 (dashed box in top left panel of \Cref{fig__jetI5+ismSeed3-45deg})\
 also extending out from the Galactic center on either side of the thin disk.\
 The innermost bubbles are cold (1-10 eV), dense ($10^{-4}$ -- $10^{-2}$ cm$^{-3}$),\
 and underpressured with respect to the turbulent plasma.
